Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-19 Thesis/chapter/062-post-emma.tex
grid search v2

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Grid Search}
For \gls{krr} and {svm} I had to find out what the ideal hyper parameters were. 
So, I anstellen a grid search with the following hyperparameters: 
%kernel=["poly","rbf"]#,"sigmoid"]
%C= np.array(range(1,20))*0.05
%degree=range(1,6)
%epsilon= np.array(range(1,20))*0.2
%gamma=[0.0,0.1,1.0,10.0]
%#param = {"kernel":kernel, "C":C, "degree":degree, "epsilon":epsilon, "gamma":gamma }
%C=[1,0.1]; degree=[3]; epsilon=[1,2]; gamma=['scale']
Now what are C,epsilon and gamma?

\td{which parameters}
The parameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid and polynomial with degree 1--4.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
The kernels for \gls{svm} were the same and further hyper parameters were 
$C$, $\varepsilon$ and $\gamma_{ml}$, where $C$ took the values 0.05--1 with 0.05 steps, $\varepsilon$ 0.02--4 with 0.2 steps and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables. 
\td{how, every combination}
Each grid search calculation was calculated with and without scaling the data before the optimisation. 
For each optimisation \gls{mae}, \gls{mse}, $sigma(\mathbf{y})$ and $\sigma(\mathbf{\hat{y}})$ were calculated.

@@

%# KRR
%# some kind of scaling factor; can be set to auto/scale, include into list? 
%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10] #HPGS
%# alpha: bigger alpha, bigger regularisation 
%alpha=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2] #, 10, 50, 100] #HPGS

% SVM
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
%# regularization parameter
%C= np.array(range(1,20))*0.05 # HPGS
%# epsilon-tube size for no penalty; rather large 
%epsilon= np.array(range(1,20))*0.2 # HPGS
%# some kind of scaling factor; can be set to auto/scale, include into list?  
%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, "scale"] # HPGS

Since the data set was very small, I could be generous with the grid search even on relatively humble hardware (intel i7-8550U).

\begin{table}[htb]
	\centering
    \caption{Post EMMA vergleich}
	\label{tab:post-emma}
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    G&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        lin Reg&    13& 250&    24& 747&    34& 1327&   17& 454\\
        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
        SVM& 15  415&    26& 1050&   28& 1588&   19& 677\\
    \hline\hline
	\end{tabular}
    %
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    p&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        lin Reg&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
    \hline\hline
	\end{tabular}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{PCR?}

@@

\subsubsection{Further}
\begin{itemize}
    \item grid search
    \item KRR (start with grid search) (???)
    \item SVM (start with grid search) (???)
    \item \url{https://blog.minitab.com/en/adventures-in-statistics-2/regression-smackdown-stepwise-versus-best-subsets}
    \item \url{https://blog.minitab.com/en/how-to-choose-the-best-regression-model}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Comparison} 
compare all methods. 
How should I compare them? 
What are the measurables.

>>>>

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Grid Search}
For \gls{krr} and {svm} I had to find out what the ideal hyper parameters were. 
So, I anstellen a grid search with the following hyperparameters: 
%
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
%# KRR
%# some kind of scaling factor; can be set to auto/scale, include into list? 
%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10] #HPGS
%# alpha: bigger alpha, bigger regularisation 
%alpha=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2] #, 10, 50, 100] #HPGS
%
% SVM
%# regularization parameter
%C= np.array(range(1,20))*0.05 # HPGS
%# epsilon-tube size for no penalty; rather large 
%epsilon= np.array(range(1,20))*0.2 # HPGS
%# some kind of scaling factor; can be set to auto/scale, include into list?  
%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, "scale"] # HPGS 
%
\td{which parameters?}
The parameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid and polynomial with degree 1--4.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
The kernels for \gls{svm} were the same and further hyper parameters were 
$C$, $\varepsilon$ and $\gamma_{ml}$, where $C$ took the values 0.05--0.95 with 0.05 steps, $\varepsilon$ 0.02--3.8 with 0.2 steps and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables.

\td{how and what?}
Each grid search calculation was calculated with and without scaling the data before the optimisation. 
For each optimisation \gls{mae}, \gls{mse}, $sigma(\mathbf{y})$ and $\sigma(\mathbf{\hat{y}})$ were calculated. 
For each method (\gls{krr} and \gls{svm}) and each kernel the parameters with the lowest \gls{mae} were chosen.

@@

%Since the data set was very small, I could be generous with the grid search even on relatively humble hardware (intel i7-8550U).

\begin{table}[htb]
	\centering
    \caption{Post EMMA vergleich}
	\label{tab:post-emma}
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    G&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        lin Reg&    13& 250&    24& 747&    34& 1327&   17& 454\\
        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
    \hline\hline
	\end{tabular}
    %
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    p&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        lin Reg&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
    \hline\hline
	\end{tabular}
\end{table}

@@

@@

\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{PCR?}
\subsubsection{Further}
\begin{itemize}
    \item grid search
    \item KRR (start with grid search) (???)
    \item SVM (start with grid search) (???)
    \item \url{https://blog.minitab.com/en/adventures-in-statistics-2/regression-smackdown-stepwise-versus-best-subsets}
    \item \url{https://blog.minitab.com/en/how-to-choose-the-best-regression-model}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Comparison} 
compare all methods. 
How should I compare them? 
What are the measurables. 
\fi

### 2023-02-19 Thesis/chapter/063-discussion.tex
start write alt cacl theory
finish theory
start Grid Seach
grid search v2

\subsection{Diskussion}
\subsubsection{Mistakes and Solutions}
This chapter is structured as a letter 
which my present self thinks that would have helped my past self 
if recieved before the start of the practical part of my master practikum:\\

to discuss: results from EMMA or rather which the data present are counter intuitive. 
why lowest conductivity with lowest TCal and why is there a minimum for layers? 
low TDOC results in lower conductivity... okay

@@

\iffalse
Dear Johann,

I know that you (I) won't believe this but I'm you in the future. 
So you are me in the past and I have a few hints on how to avoid some stone in your way 
and how to hopefully be more successful in you master thesis. 
"I make a plan. I break a plan. But I'm never without a plan." - a nice quote which I couln't zuschreiben, but which holds a lot of truth. 
Planning can give you the chance to zoom out and force yourself to get an overview. 
It let's you decide how much time you want to spend on each todo.

The next tip is that at the beginning of a project the research phase shouldn't be underestimated. 
Take time to dig into the basics and discuss with colleagues if you have the chance. 
Try to understand the methods you'll use as well as possible. 
Most importantly, high light advantages and disadvantages of the methods and competing/alternatives. 
Like in a design project. Lay out as many as diverse solutions as possible, 
compare, and ick the best parts.
The research phase let's you learn from other's mistakes and saves a lot of time.

Another important task which preceeds/anti-follows above mentioned is to define the objective as clear as possible.  
%\td{ideal objective is to create response surface approximation}\\
It will help to set a clear goal for each todo, e.g. 
the primary goal of a screening experiment is to identify the active factors.\cite{miller2001using}
Which question should be answered and aufstellen a null Hypothesis. 
This is often very trivial, but let's you focus on the correct path.

@@

>>>>

\subsection{Discussion}
\subsubsection{Mistakes and Solutions}
%This chapter is structured as a letter 
%which my present self thinks that would have helped my past self 
%if recieved before the start of the practical part of my master practikum:\\

%to discuss: results from EMMA or rather which the data present are counter intuitive. 
%why lowest conductivity with lowest TCal and why is there a minimum for layers? 
%low TDOC results in lower conductivity... okay 
\subsubsection{ad results}
why correlation $\gamma$?
\subsubsection{tips for next time}
\begin{itemize}
    \item \textbf{planning} gives chance of zooming out, force oneself to get an overview and to decide how much time on each task
    \item \textbf{research} phase is most important, dig into basics, discuss ideas with colleagues or go into detail about plan. Understand details of methods. Make a dummy run. Collect (dis-)advantages of different methods. Like in design project: do as many and as deverse solutions as possbile. Compare and combine the best parts. Reading will let learn from others mistakes. 
    \item \textbf{objective} should be defined as clear as possible. It will help to set a clear goal for each todo, e.g. the primary goal of a screening experiment is to identify the active factors.\cite{miller2001using} Which question should be answered and aufstellen a null Hypothesis. This is often very trivial, but let's you focus on the correct path. 
    \item \textbf{keep it simple}

\end{itemize}

@@

@@

\td{don't try to solve a problem by solving a more general problem}
\td{search i.e. and replace with i.e.\ }
